Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
paper: add result to abstract
Related work section

The distributed metadata service in Ceph provides clients with a POSIX file
system abstraction~\cite{weil:sc2004-dyn-metadata}. In general, distributed
file systems protect resources by providing hierarchical indexing and
distributed locking services.  In Ceph, the locking service implements a
capability-based system that express what data and metadata clients are allowed
to access as well as what state they may cache and modify locally. While
designed for a fixed file abstraction, indexing, locking, and caching are all
common services that are useful to a broad spectrum of applications.

Ceph also addresses the challenge of balancing metadata load using load
balancing policies that compute metrics based on system state (e.g.  CPU and
memory utilization) and statistics collected by the cluster (e.g. the
popularity of an inode). Ceph uses dynamic subtree partitioning to move
variable sized namespace subtrees. These units can be shipped anywhere (i.e.,
to any MDS of any capacity) at any time for any reason. The original balancer
was designed with hard-coded policies and tunables.  Distributed applications
that share centralized resources (e.g. a database or directory) face similar
challenges which are often solved using application-specific sharding.

%The metadata cluster moves units of the namespace called directory fragments
%and assigns them to servers using its own metadata load balancer. It then uses
%a hard-coded policy to balance these fragments using a scalarized load metric
%based on CPU, workload, and file system operation metrics. Although the CephFS
%balancer has been shown to be complicated, its complexity is justifiable.
%Having the flexibility to choose what to move, where to move it, and how much
%to move is very powerful. The problem is that it is difficult to pick a
%one-size-fits-all policy, system administrators may want to partition load
%based on SLAs, or applications are better equipped to make these decisions,
%etc. -- but we choose instead to expose a balancing API at strategic points in
%the balancing logic using Lua hooks. ~\cite{sevilla:sc15-mantle}.

\paragraph*{Malacology:} New interface hooks are added in strategic spots in
the metadata service to control load balancing and capabilities, and for
defining new file types allowing the indexing service to be repurposed for
other types of named resources.

{\bf Load balancing.} Mantle~\cite{sevilla:sc15-mantle}, a programmable
metadata load balancer, has been re-implemented on Malacology so that its
infrastructure can enjoy all the properties of other Ceph components. The load
balancing logic has stayed largely the same but the infrastructure has been
improved to safely load, manage, and persist its load balancing policies.

{\bf Safely Loading Classes.} The original Mantle API is fragile: the API is
not enforced by the runtime, the system allows injectable strings through the
admin daemon, constructing the Lua script in C++ is clunky, and the
administrator can inject really bad policies (e.g., while 1) that brings the
whole system down. Malacology exposes the important subsystems of Ceph's
logical storage device framework so that the MDS can safely and dynamically
load policies specified as Lua classes.

{\bf Policy management.} A new interface is added to the metadata service
subsystem using the monitoring framework to support management of interfaces. This 
ensures that the correct balancer version is consistently distributed and verified on
all MDS nodes. Policies are also durably saved with Ceph's replication and redundancy.

%These problems are general, distributed systems load balancing problems and
%share many of the same properties as the POSIX metadata
%wall~\cite{alam:pdsw2011-metadata-scaling,ghemawat:sosp2003-gfs,hildebrand:msst2005-pnfs,weil_ceph_2006,welch:fast2008-panasas,shvachko:login2012-hdfs-scalability}.
%Many distributed file systems decouple metadata and data I/O so that these
%services can scale independently. Despite this optimization, scaling the
%metadata services is still difficult because metadata accesses impose small
%and frequent requests on the underlying storage
%system~\cite{roselli:atec2000-FS-workloads}. Many techniques for designing the
%metadata services have been proposed to accommodate this workload:
%Lustre~\cite{konstantinos:pdsw2014-lustre-metadata},
%GFS~\cite{ghemawat:sosp2003-gfs}, and
%HDFS~\cite{shvachko:login2012-hdfs-scalability} keep all metadata on one
%server; GIGA+~\cite{patil:fast2011-giga}, IndexFS~\cite{ren:sc2014-indexfs},
%Lazy Hybrid~\cite{brandt:msst2003-lh}, GPFS~\cite{schmuck:fast2002-gpfs}, and
%pNFS~\cite{hildebrand:supercomputing2006-pNFS} hash the file system namespace
%across a dedicated cluster and cache metadata;
%Panasas~\cite{welch:fast2008-panasas} and
%CephFS~\cite{weil:sc2004-dyn-metadata} use subtree partitioning to carve up
%the namespace and distribute it across a cluster.
%
%Both the object and balancer interfaces define functions and attach them
%to the core Lua sandbox. For example, the Lua object storage interface
%class attaches data, extended attribute, object map, and object version
%functions, to the Lua core functions, as shown in Figure
%\ref{fig:cls-osd-mds}. The advantages of this is that we avoid
%duplicating code, we provide a framework for putting Lua code in other
%parts of the system, and we remove components and APIs that are too
%integrated with the OSD.

%To facilitate the use of Lua in both the MDS and OSD, we modularize the LuaVM
%in a core sandbox wrapper and link against it, as shown in
%Figure~\ref{fig:cls-osd-mds}. This core Lua wrapper contains just the
%dependencies, symbols, and functions, needed to run the Lua VM and strips away
%all the functionality inherent to object classes (like placement group
%filters, cryptography functions, object metadata,  object data, object
%extended attributes, and object versions). Some functions of Ceph's more
%helpful subsystems, like the logging facilities for the daemons, were re-used
%in the MDS.  With this scheme, The OSD will dynamically open the shared
%library created by Lua object interface shared library while the MDS will
%dynamically open the Lua balancer interface shared library; both shared
%libraries will the Lua core.

{\bf Capabilities.} The metadata service also manages sessions with its
clients. This gives both subsystems (MDSs and clients) the ability to cache
data and grab locks. The metadata service is responsible for responding to
client requests for capabilities by first revoking caps from other clients.
Currently, clients voluntarily release their capabilities, and the MDS maintains
a queue of requests.  Both clients and MDSs use a best-effort approach to
revoking or releasing capabilities.

The clients retain the best-effort, voluntary release of capabilities, but in
Malacology, the queuing policies are generalized within the MDS to allow for
centeralized policies such as fairness or priority.

{\bf File Types.} We leverage the same active and typed storage module
presented in DataMods~\cite{watkins_datamods_2012} to assign state and a set of
functions to a file (stored in the inode). This is valuable for
metadata load balancing so that certain types of files can have a higher
priority when making balancing decisions.

%\begin{figure}[h]
%\centering
%\includegraphics{figures/cls-osd-mds.png}
%\caption{To generalize the LuaVM for use in both the OSD and MDS,
%Malacology detaches the core functionality into a Lua core module. The
%VM is dynamically loaded first (1) and then interfaces can execute (2).
%\label{fig:cls-osd-mds}}
%\end{figure}

@@

The Ceph team wants to merge Mantle because the scriptability is useful for
debugging, controlling the metadata balancer, and examining trade-offs for
different balancers. Unfortunately, this research quality system is not as
robust as Ceph and the Ceph team wants more safety, durability, and consistency
for the new services.  The API for Malacology is the same as the one exposed
in~\cite{sevilla:sc15-mantle} but the hooks are put in different places.

@@

>>>>

The distributed metadata service in Ceph provides clients with a POSIX file
system abstraction~\cite{cephfs}. Distributed file systems are complex, but
fundamentally provide hierarchical indexing and distributed locking services.
In Ceph, the locking service implements a capability-based system that express
what data and metadata clients are allowed to access as well as what state
they may cache and modify locally. While designed for a fixed file
abstraction, indexing, locking, and caching are all common services that are
useful to a broad spectrum of applications.

Ceph addresses the challenge of balancing load across the metadata cluster
using load balancing policies that compute balancing metrics based on system
state (e.g. CPU and memory utilization) and statistics collected by the
cluster (e.g. the popularity of an inode). Distributed applications that share
centralized resources (e.g. a database or directory) face similar challenges
which are often solved using application-specific sharding.

\paragraph*{Malacology:}
Malacogy adds interface hooks in strategic spots in the metadata service to
control load balancing, capability subsystems, and for defining new file
types allowing the indexing service to be repurposed for other types of
named resources.

{\bf Load balancing.}
For CephFS, designing a general POSIX metadata load balancer is difficult
becuase the workloads are diverse and quickly changing. With CephFS, it is
especially complicated because the system has variable sized migration units
(i.e. file system namespace subtrees), which can be shipped anywhere (i.e., to
any MDS of any capacity) at any time for any reason. Furthermore, the original
balancer was designed with hard-coded policies and tunables. Both angles were
difficult to understand. It is understandable why it was implemented this way
-- it is difficult to pick a one-size-fits-all policy, system administrators
may want to partition load based on SLAs, or applications are better equipped
to make these decisions, etc. -- but we choose instead to expose a balancing
API at strategic points in the balancing logic using Lua hooks.

These problems are general, distributed systems load balancing problems and
share many of the same properties as the POSIX metadata
wall~\cite{alam:pdsw2011-metadata-scaling,ghemawat:sosp2003-gfs,hildebrand:msst2005-pnfs,weil_ceph_2006,welch:fast2008-panasas,shvachko:login2012-hdfs-scalability}.
Many distributed file systems decouple metadata and data I/O so that these
services can scale independently. Despite this optimization, scaling the
metadata services is still difficult because metadata accesses impose small
and frequent requests on the underlying storage
system~\cite{roselli:atec2000-FS-workloads}. Many techniques for designing the
metadata services have been proposed to accommodate this workload:
Lustre~\cite{konstantinos:pdsw2014-lustre-metadata},
GFS~\cite{ghemawat:sosp2003-gfs}, and
HDFS~\cite{shvachko:login2012-hdfs-scalability} keep all metadata on one
server; GIGA+~\cite{patil:fast2011-giga}, IndexFS~\cite{ren:sc2014-indexfs},
Lazy Hybrid~\cite{brandt:msst2003-lh}, GPFS~\cite{schmuck:fast2002-gpfs}, and
pNFS~\cite{hildebrand:supercomputing2006-pNFS} hash the file system namespace
across a dedicated cluster and cache metadata;
Panasas~\cite{welch:fast2008-panasas} and
CephFS~\cite{weil:sc2004-dyn-metadata} use subtree partitioning to carve up
the namespace and distribute it across a cluster.

CephFS moves units of the namespace called directory fragments and assigns
them to servers using  its own metadata load balancer. It then uses a
hard-coded policy to balance these fragments using a secularized load metric
based on CPU, workload, and file system operation
metrics~\cite{sevilla:sc15-mantle}.

Both the object and balancer interfaces define functions and attach them
to the core Lua sandbox. For example, the Lua object storage interface
class attaches data, extended attribute, object map, and object version
functions, to the Lua core functions, as shown in Figure
\ref{fig:cls-osd-mds}. The advantages of this is that we avoid
duplicating code, we provide a framework for putting Lua code in other
parts of the system, and we remove components and APIs that are too
integrated with the OSD.

To facilitate the use of Lua in both the MDS and OSD, we modularize the LuaVM
in a core sandbox wrapper and link against it, as shown in
Figure~\ref{fig:cls-osd-mds}. This core Lua wrapper contains just the
dependencies, symbols, and functions, needed to run the Lua VM and strips away
all the functionality inherent to object classes (like placement group
filters, cryptography functions, object metadata,  object data, object
extended attributes, and object versions). Some functions of Ceph's more
helpful subsystems, like the logging facilities for the daemons, were re-used
in the MDS.  With this scheme, The OSD will dynamically open the shared
library created by Lua object interface shared library while the MDS will
dynamically open the Lua balancer interface shared library; both shared
libraries will the Lua core.

{\bf Capabilities.}
The metadata service also manages sessions with its clients. This gives both
subsystems (MDSs and clients) the ability cache data and grab locks. The
metadata service is responsible for responding to client requests for
capabilities by first revoking caps from other clients. Currently clients
voluntarily release their capabilities, and the MDS maintains a queue of
requests.  Both clients and MDSs use a best-effort approach to revoking or
releasing capabilities.

In our current we retain the best-effort, voluntary release of caps within
clients, but generalize the queueing policies within the MDS to allow for
centeralized policies such as fairness or priority.

{\bf File Types.}
We can reference PDSW12 DataMods, and talk about any new stuff here that we
want to.

{\bf Policy management.} A new interface is added to the metadata service
subsystem using the monitoring framework to support management of interfaces,
which ensures durability and distribution of policies in a consistent way.

\begin{figure}[h]
\centering
\includegraphics{figures/cls-osd-mds.png}
\caption{To generalize the LuaVM for use in both the OSD and MDS,
Malacology detaches the core functionality into a Lua core module. The
VM is dynamically loaded first (1) and then interfaces can execute (2).
\label{fig:cls-osd-mds}}
\end{figure}

@@

The Ceph team wants to merge Mantle because the scriptability is useful
for debugging, controlling the metadata balancer, and examining
trade-offs for different balancers. Unfortunately, this research quality
system is not as robust as Ceph and the Ceph team wants more safety,
durability, and consistency for the new services. For example, the
original Mantle API is fragile: the API is not enforced by the runtime,
the system allows injectable strings through the admin daemon,
constructing the Lua script in C++ is clunky, and the administrator can
inject really bad policies (e.g., while 1) that brings the whole system
down.

The API for Malacology is the same as the one exposed in~\cite{sevilla:sc15-mantle} but the hooks are put in different places using the interface hooks described in Section \S\ref{}.

@@

Programmability of operating systems and networking resources, including distributed storage systems is not new, but we are not aware of work that makes generalization of existing services into programmable resourses a key principle in storage systems design.

Programmable storage systems can be viewed as an infrastructure for creating abstractions to better separate policies from mechanisms. This idea is not new. Software-defined networks (SDNs) create such an abstraction by separating the control plane from the data plane (see for example~\cite{jain:sigcomm13}). This notion of control/data separation was also applied in software-defined storage (SDS)~\cite{arpaci:sosp01,thereska:sosp13,stefanovici:fast16}. Similarly, IOStack~\cite{gracia:internet16} is providing policy-based provisioning and filtering in OpenStack Swift.

Another view of programmable storage systems is one of tailoring systems resources to applications~\cite{arpaci:sosp01}. Related work includes work around the Exokernel~\cite{engler:sosp95} and SPIN~\cite{bershad:sosp95} and Vino~\cite{seltzer:osdi96}, the latter two addressed the ability of injecting code into the kernel to specialize resource management. Another approach is to pass hints between the different layers of the IO stack to bridge the semantic gap between applications and storage~\cite{arpaci:sosp01,sivathanu:fast03,mesnier:sosp11}).

Malacology uses the same Active and Typed Storage module presented in
DataMods~\cite{watkins_datamods_2012}; Asynchronous Service and File
Manifolds can be implemented with small changes to the Malacology
framework, namely asynchronous object calls and Lua stubs in the inode,
respectively.
